---
title: "Project 1_re"
author: "Xinwei Hu"
date: "5/20/2021"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
#Read the dataset
library(e1071)
churner<- read.csv("/Users/matthu/Desktop/BankChurners.csv")
head(churner)
```


```{r}
#Detecting NA
nrow(churner)
churner=na.omit(churner)
nrow(churner)

churner$Attrition_Flag <- as.factor(churner$Attrition_Flag)

churner$Gender <- as.factor(churner$Gender)

churner$Education_Level <- as.factor(churner$Education_Level)

churner$Marital_Status <- as.factor(churner$Marital_Status)

churner$Income_Category <- as.factor(churner$Income_Category)

churner$Card_Category <- as.factor(churner$Card_Category)
```
```

```{r}
summary(churner$Customer_Age)
summary(churner$Months_on_book)
summary(churner$Dependent_count)
```


In this part, we have classified three numerical variable, age, months and dependent.

```{r}
# classify numerical data
# age from 25 to 75, we classify to three types
age_class <- function(age){
  if(age>=25 && age<=35){
   age = "25-35"
  } 
  if(age>=36 && age<=50){
   age = "36-50"
  }
  if(age>=51 && age<=75){
  age = "51-75"
  }
  age
}
churner$age_class <- mapply(age_class,churner$Customer_Age)

months_class <- function(Months_on_book){
  if(Months_on_book>=12 && Months_on_book<=35){
   Months_on_book = "12-35"
  } 
  if(Months_on_book>=36 && Months_on_book<=47){
   Months_on_book = "36-47"
  }
  if(Months_on_book>=48 && Months_on_book<=60){
  Months_on_book = "48-60"
  }
  Months_on_book
}
churner$months_class <- mapply(months_class,churner$Months_on_book)

dependent_class <- function(dependent){
  if(dependent==0){
   dependent = "0"
  } 
  if(dependent==1){
   dependent = "1"
  }
  if(dependent==2){
  dependent = "2"
  }
  if(dependent==3){
  dependent = "3"
  }
  if(dependent==4){
  dependent = "4"
  }
  if(dependent==5){
  dependent = "5"
  }
  dependent
}
churner$dependent_class <- mapply(dependent_class,churner$Dependent_count)


head(churner)
```


```{r}
set.seed(128)
# Create training and validation sets.
selected.var <- c(2, 4, 6, 7, 8, 9, 11, 12, 13)
train.index <- sample(c(1:dim(churner)[1]), dim(churner)[1]*0.6)  
train.df <- churner[train.index, selected.var]
valid.df <- churner[-train.index, selected.var]
head(train.df)
head(valid.df)
```

In the following part, we have run the naive bayes of conditional probabilities

```{r}
# Run naive bayes: Conditional Probabilities which can be computed directly from the data
churner.nb <- naiveBayes(Attrition_Flag ~ ., data = train.df)
churner.nb
```


```{r}
# Predict Probabilities
pred.prob <- predict(churner.nb, newdata = valid.df, type = "raw")
## Predict class membership
pred.class <- predict(churner.nb, newdata = valid.df)
df <- data.frame(actual = valid.df$Attrition_Flag, predicted = pred.class, pred.prob)
head(df)
```

```{r}
# Evaluate Performance
library(caret)
# Training
pred.class <- predict(churner.nb, newdata = train.df)
confusionMatrix(pred.class, train.df$Attrition_Flag)
```

In the train set, we have found the accurary is 0.7018.

```{r}
# Validation
pred.class <- predict(churner.nb, newdata = valid.df)
confusionMatrix(pred.class, valid.df$Attrition_Flag)
```

In the validation set, we have found the accuracy is 0.6859.

